Title

### 2013-02-25 inc/extension/initial_conditions/bin_model_figure.tex
comment on bin model
more improvements to initial_conditions section

\begin{figure}
  \centerline {
    \subfloat[][]{
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
\end{figure}

>>>>

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:bin_model_acc}
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:bin_model_vmax}
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \label{fig:bin_model_equal}
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
  \caption[Results of bin model for computing initial conditions]{
    Comparison of the results of the bin model and AG model allowed functional forms for three different input parameters cases.
    Compared are: \subref{fig:bin_model_acc} the DC acceleration dominated case, \subref{fig:bin_model_vmax} the photoemission energy dominated case, and \subref{fig:bin_model_equal} an intermediate case.
    For $\sigma_z$ (red) and $\gamma_z$ (green) the simulated data (solid) and the fit to the AG allowed form (dashed) are decently well matched in all cases.
    Unfortunately, the model only allows for a constant $\eta_z$ (green) and in all but the extreme acceleration dominated case \subref{fig:bin_model_acc} the model cannot well represent the simulated data.
  }
  \label{fig:bin_model}
\end{figure}

### 2013-02-25 inc/extension/initial_conditions/initial_conditions.tex
more improvements to initial_conditions section

\subsection{Iterative Spatial/Temporal Bin Model}

@@

\input{bin_model_figure}

@@

Additionally the iterative time-step analysis clearly demonstrates that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the mean-field theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch.
Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: %TODO reference bin model
indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

>>>>

\subsection{Iterative Spatial/Temporal Bin Model} \label{sec:bin_model}

@@

\input{bin_model_figure} %TODO do another run of this data, so I can have the run parameters

@@

Additionally the iterative time-step analysis clearly demonstrates that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the self-similar theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch; to allow a more realistic fit to the simulated initial data, the pulse would eventually evolve to be non-Gaussian.
%Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.
